---
title: "R Notebook"
output: html_notebook
---

```{r}

```{r}
#setup multitheading
library(doParallel)

cores = detectCores()


```


```{r}

library(dplyr)
library(tidymodels)
library(usemodels)
## Assume you save the training data in the folder "C:/temp" in your local laptop
traindata <- read.table(file = "C:/temp/7406train.csv", sep=",");
dim(traindata);
## dim=10000*202
## The first two columns are X1 and X2 values, and the last 200 columns are the Y valus

### Some example plots for exploratory data analysis
### please feel free to add more exploratory analysis
testX  <- read.table(file = "C:/temp/7406test.csv", sep=",")
names(traindata)[names(traindata) == 'V1'] = 'X1'
names(traindata)[names(traindata) == 'V2'] = 'X2'
names(testX)[names(testX) == 'V1'] = 'X1'
names(testX)[names(testX) == 'V2'] = 'X2'
X1 <- traindata[,1];
X2 <- traindata[,2];

## note that muhat = E(Y) and Vhat = Var(Y)
muhat <- apply(traindata[,3:202], 1, mean);
Vhat  <- apply(traindata[,3:202], 1, var)

data0 = data.frame(X1 = X1, X2=X2, muhat = muhat, Vhat = Vhat)


```



```{r}
#tidy models learning stuff

set.seed(123)


#splitting data
split = initial_split(data0)
train = training(split)
test = testing(split)

set.seed(234)
folds = bootstraps(train)

```

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```

